A weakly structured stem for human origins in Africa

### 2023-01-16 paper.tex
Fixed validation sentence
Erroneous citations, awk wording, incorrect aspersions. 685-691

We also find that Stem 2 continued to contribute to western Africans during the
Last Glacial Period, indicative that this gene flow likely occurred in
western/central Africa (Table~\ref{tab:migration-rates}). Such an
interpretation is reinforced by the differential migration rates between
regions, i.e. the gene flow from Stem 2 to western Africans is estimated to be
five times that of the rate to eastern Africans during this period. We
performed a variety of validation tests to explore sensitivity of our
assumptions, including relaxing fixed parameters (SI
Section~\ref{sec:validation_strategy}). Most validation tests resulted in
parameters similar to the models discussed above. However, one exception was
the inferred Out-of-Africa and eastern/western African divergences which were
10-15ka younger than our fixed parameters, seemingly at odds with the
archaeological record \citep{Hublin2020-nk,Hajdinjak2021-jo} and some
genetic estimates \citep{Schlebusch2017-nl,Kamm2020-vn}. The likely
complexity of the demographic events that we model as population splits
warrants the inclusion of additional Eurasian populations and greater modeling
detail, particularly for the Out-of-Africa expansion. However, other features
of our inferred models are weakly affected by this analysis choice.

>>>>

We also find that Stem 2 continued to contribute to western Africans during the
Last Glacial Period, indicative that this gene flow likely occurred in
western/central Africa (Table~\ref{tab:migration-rates}). Such an
interpretation is reinforced by the differential migration rates between
regions, i.e. the gene flow from Stem 2 to western Africans is estimated to be
five times that of the rate to eastern Africans during this period. We
performed a variety of validation tests to explore sensitivity of our
assumptions, including relaxing fixed parameters (SI
Section~\ref{sec:validation_strategy}). Most validation tests resulted in
parameters similar to the models discussed above. However, one exception was
the inferred Out-of-Africa and eastern/western African divergences which were
10-15ka younger than our fixed parameters. The
complexity of the OOA expansion warrants the inclusion of additional Eurasian populations 
and more detailed modeling. However, other features
of our inferred models are weakly affected by this analysis choice.
